---
output: rmarkdown::github_document
---

`lodes` :  Retrieve Data from LEHD Origin-Destination Employment Statistics Server

The following functions are implemented:

- `read_lodes`:	Retrieve a LODES file/data
- `read_xwalk`:	Retrieve geography crosswalk for a state

Both functions take a `download_dir` parameter and local copies of the remote files
will be cached to that directory and read from vs re-downloading (be kind to servers).
Remove the file if you want a fresh version.

### Installation

```{r eval=FALSE}
devtools::install_git("https://github.com/hrbrmstr/lodes.git")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(lodes)
library(dplyr)

# current verison
packageVersion("lodes")

# Grab a crosswalk file
id_xwalk <- read_xwalk("id", "~/Data/lodes")

glimpse(id_xwalk)

# Some different params
de <- read_lodes("de", "od", "aux", "JT00", "2006", "~/Data/lodes")
glimpse(de)

ak <- read_lodes("ak", "residence", "S000", "JT00", "2002", "~/Data/lodes")
glimpse(ak)

id <- read_lodes("id", "workplace", "SE02", "JT03", "2013", "~/Data/lodes")
glimpse(id)
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(lodes)
library(testthat)

date()

test_dir("tests/")
```

